---
title: "Lab 00 - Hello IDS!"
author: "Cameron Fisher"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Finlay Webb", "Harry English", "Ed Kimber", 
           "Tom Cummings", "Finn McLachlan", "Evan Howe"),
  github_username = c("finlaydwebb", "harryenglish", "edkimber", 
                      "tom-rex", "finnmc3", "evanh05"), 
  colour = c("green", "blue", "red", 
             "red", "blue", "blue"),
  hobby = c("eating", "sleeping", "cricket", 
            "nuisance", "walking up stairs", "cricket"),
  favourite_number = c(1.3, 6.02, 7, 9, 2.5, 6.6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The bar graph is showing the groups favourite numbers against their usernames, as well as their favourite colours.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite number",
          title = "Group 9")
```

Labs changes the labels of a graph, i.e. title, axis names.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

There are too many bars for it to look clean/easy-to-read, it could possibly be displayed using a pie chart or just a general table (allowing for each of the hobbies to be idnetified as well as the number per hobby being shown also)
